Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-10-21 referee.tex
Finished revising responses

V -- The authors give three reasons for the halo mass spread. Can they estimate which of the three processes (BH formation, dynamical heating and temporal LWBG fluctuations) is responsible for the spread by which fraction?
\end{referee}

This is an interesting question, but it is outside the scope of this paper.  It most likely depends on the large-scale environment, halo mass accretion history, and halo star formation history, but how these factors affect each other is unclear.  In practice, it would be difficult to determine the relative importance of dynamical heating and temporal LWBG fluctuations because of the time variations in the heating rate and suppression of H$_2$ cooling.  Because of these reasons, we do not give any estimates in the discussion.

@@

\begin{referee}
W -- One of the most extensive studies on over 1000 minihaloes was performed by Hirano+15, who also include a Lyman-Werner background. Their work should be put in comparison as well.
\end{referee}
This study has been added and cited in the Comparison section.
\textbf{-Should more be added?}

@@

\begin{referee}
Y -- Since the authors study star formation in minihaloes, it would be appropriate to also mention Kitayama+04 and Schauer+15 for the Lyman-Werner escape fractions from minihaloes.
\end{referee}
These papers have been added and referenced in the first paragraph of the caveats section.

\begin{referee}
Z -- The authors mention a few times that streaming velocities are another pathway of suppressing Pop III formation (also in the introduction). While they cite some older work, they however fail to compare to more recent work eg by Hirano+18 or Schauer+19 (who do perform a systematic study not only based on a few, single haloes).
\end{referee}
The Schauer+19 study has been added to the caveat section.

>>>>

V -- The authors give three reasons for the halo mass spread. Can they estimate which of the three processes (BH formation, dynamical heating and temporal LWBG fluctuations) is responsible for the spread by which fraction?
\end{referee}
This is an interesting question, but it is outside the scope of this paper.  It most likely depends on the large-scale environment, halo mass accretion history, and halo star formation history, but how these factors affect each other is unclear.  In practice, it would be difficult to determine the relative importance of dynamical heating and temporal LWBG fluctuations because of the time variations in the heating rate and suppression of H$_2$ cooling.  Because of these reasons, we do not give any estimates in the discussion.

@@

\begin{referee}
W -- One of the most extensive studies on over 1000 minihaloes was performed by Hirano+15, who also include a Lyman-Werner background. Their work should be put in comparison as well.
\end{referee}
We have added the results from Hirano et al. (2015) to our comparison to other work in the discussion.

@@

\begin{referee}
Y -- Since the authors study star formation in minihaloes, it would be appropriate to also mention Kitayama+04 and Schauer+15 for the Lyman-Werner escape fractions from minihaloes.
\end{referee}
We have added and cited these papers in the first paragraph of the caveats subsection.

\begin{referee}
Z -- The authors mention a few times that streaming velocities are another pathway of suppressing Pop III formation (also in the introduction). While they cite some older work, they however fail to compare to more recent work eg by Hirano+18 or Schauer+19 (who do perform a systematic study not only based on a few, single haloes).
\end{referee}
We have also added the Schauer et al. (2019) study to the caveats subsection.
